Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-08 Ben_Manuscripts/structure_paper/Draft.tex
new figures

  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections of R-$\pi$ 
  are in moderate agreement with experiment (Figure~\ref{fig:rpi_exp_comparison}). The
  FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the $q_r$ cross-section
  FWHM is 21\% larger than experiment. Note that the experimental data is best fit with a Lorentzian 
  function while the simulated patterns are best fit using a Gaussian function. The simulated
  spectra do not incorporate the effects of pressure broadening and instrumental broadening
  which would alter the peak shape. In the absence of these and other peak broadening effects,
  the experimental peak would actually be narrower, further increasing the discrepancy with simulation.

  %MRS9: State explicitly in what way the discrepancy would increase, i.e. experimental FWHM are broadened by other source (doppler pressure, insttrument broadening) that do no affect the simulated spectra, the experimental spectra may be even narrower than spectra generated from simulations are.  
  %MRS9: one question, do any of the approximations used in the simulation actually lead to broadening that would not be in experiment (gaussian scatterers, etc.  Also, (semi-related) do Gaussian scatters lead to Gaussian peaks? Fourier transforms of Gaussians are Gaussians) 
  % BJC8: Can add more detail about different types of broadening - instrument / finite resolution broadening (for
  % experimental case), doppler (gaussian shaped) and pressure broadening (Lorentzian shaped)
  % See: https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-7
  %MRS 9: it is a little problematic to use two different types of fit, as the FWHM is a little different for each of then. Would lead to slight discrepancies from that.  FWHM is a natural scale parameter for Lorenzians, but not really for Gaussian.  
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.194 $\pm$ 0.013 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.962 $\pm$ 0.010 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \caption{
  In experiments ((a) and (b)), (a), R-$\pi$ broadens in the $q_z$ direction with a FWHM of 
  0.110 $\pm$ 0.003 $\AA^{-1}$ when fit with a Lorentzian function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792 
  $\pm$ 0.009 $\AA^{-1}$ when fit with a Lorentzian function. In our simulations ((c) and (d)), (c) the FWHM of R-$\pi$ in
  the $q_z$ direction is 0.194 $\pm$ 0.013 $\AA^{-1}$ when fit with a Gaussian function, nearly twice the width
  of experiment. (d) The simulated FWHM in the $q_r$ direction is 0.962 $\pm$ 0.01 $\AA^{-1}$ when fit with
  a Gaussian function, about 20 \% larger than experiment. Note that the large spike in the center is not included
  in the fit.}\label{fig:rpi_exp_comparison}
  \end{figure}

  %MRS9: Could be stronger thesis.  Suggest
  We have identified a number of potential ways that simulation conditions, forcefield 
  and initial configurations could affect the intensity of R-$\pi$ as well its FWHM in 
  the $q_z$ and $q_r$ directions. We assessed each using a simplified model. Our 
  simplified model represents each monomer head group as a single point and places them
  in either a parallel displaced or sandwiched configuration. We chose to explore
  the influence of thermal noise in each dimension, correlation between scatterers within
  columns, as well as correlation between columns since these are the variables we 
  believe have the largest influence on peak shape.
  %MRS9: probably best to focus on the variables that we think could cause a problem (i.e. hypotheses to test) first, then talk about how the experiments tested these hypotheses.

  As a baseline, we created a simplified model using the same amount of disorder present
  in our atomistic simulations. There are two sources of disorder to consider: thermal motion of
  atoms and quenched disorder which is created by rapid structural rearrangement during
  early equilibration and is locked into place for the remainder of the simulation time. The
  latter has important implications for the reproducibility of this work since both initial
  configurations and velocity randomization at the beginning of equilibration can lead to
  different quenched configurations. We measured thermal disorder by measuring the standard 
  deviation in the distribution of head group center of mass positions from their average 
  positions. We measured quenched disorder by calculating the standard deviation of the 
  distribution of head group center of masses from their idealized average positions. In the
  $z$-direction, we measured the deviation of the head group center of masses from an equally
  spaced column of head groups. In the $xy$ plane, we calculated the deviation in radial 
  position from the pore center and the angular deviation from equally spaced points surrounding
  the pore center. The values measured for each system are given in Table~\ref{table:quenched_disorder}.
  Using these parameters, we built a trajectory consisting of 1000 independent configurations. 
  We also made the simple system 4 times taller in order to get better resolution in the $q_z$ 
  direction. Figure~\ref{fig:sf_qy_nocorrelation} shows the $q_y$ cross-section of R-$\pi$ 
  generated by simulating the structure factor of the trajectory.

@@

%MRS9: sorry, I keep reading ``no correlation'' as ``no collusion'' :)
%BJC9: haha^
%BJC9: I could probably get rid of qy cross-sections and inset in (c)
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
  \caption{}\label{fig:sf_qy_nocorrelation}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
  \caption{}\label{fig:sf_qy_correlation.png}
  \end{subfigure} 
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
  \caption{}\label{fig:sf_qz_correlation.png}
  \end{subfigure}   
  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
  points meant to represent monomer head groups. We added a similar amount of noise to 
  that seen in our simulations. (a) We added Gaussian noise to each particle in the $z$, 
  $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
  peaks. (b) When we make points in each column correlated, the intensity of R-$\pi$ 
  increases but the sharp peaks remain with the same ratio of intensity between the
  center and outer peaks. (c) 
  %MRS9: I'm not sure what you mean by ``correlation'' broadening peaks here.  Do you mean replacing exact periodicity by 
  %correlated random points  Because that reduces correlation (from 100% to less than 100%).
Correlation between scatterers in the $z$-direction causes
  R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
  % MRS9: in c, weird that the orange peaks are broader, but taller. Not sure I understand.
  % BJC9: Good catch, not sure why I didn't question that. Was inputting square root of standard deviation 
  % rather than square of standard deviation as variance, so there was less noise. Fixed now.
  % BJC9: Heights are still slightly different after 1000 independent configurations
  % BJC9: Shape is also different. Looks like the points are more evenly spaced in correlated
  % system so there are less points at high and low q.
  \end{figure}

  Scatterers in each column are correlated with each other. In the simplified 
  system described above, we added uncorrelated Gaussian noise in the 
  z-direction which ignores any interaction head groups might have with each
  other. To remedy this, we randomly sampled a multivariate normal distribution
  with the same standard deviation, $\sigma$ shown in by Table~\ref{table:quenched_disorder}. We 
  defined the distribution using a covariance matrix such that the covariance, v,
  in position, z, between scatterers decays exponentially from v according to the
  equation $ve^{-z/L}$, where L is the correlation length. Experimentally, the
  correlation length can be estimated as the inverse of the FWHM of the $q_z$
  cross-section of R-$\pi$.  %BJC8: needs references 
  Accordingly, the correlation length of the experimental system is $\geq$ 9 
  $\AA$. The value may be larger since the peak is likely broadened for a variety
  of other reasons. %BJC8: the reasons I can provide more detail on above.  
  %BJC8: Can show correlation effect on intensity in supporting info

@@

  Increased thermal noise in the $z$-direction causes a drop in the intensity of R-$\pi$, however 
  the $q_r$ profile remains unchanged. When we increase the thermal noise in the $z$-direction by
  11\% and 28\%, we see a 3 and 15 fold decrease in the intensity of R-$\pi$ respectively (Figure
  ~\ref{fig:znoise}). Despite the decrease in intensity, the 3 cross-sections have the same shape,
  whose sharp Bragg-like peaks are not consistent with experiment. The peaks are spaced apart
  according to the pore spacing, and line up with R-alkanes. The center of mass of all columns in
  our initial configuration are situated at the z coordinate.

  % BJC9: could overlay these plots, but might look messy. Maybe there is a more compact representation
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_correlation.png}  %BJC9: z_variance = 2.074 angstroms
  \caption{}\label{fig:sf_znoise_control}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_3xdecrease.png}  %BJC9: z_variance = 2.55 angstroms
  \caption{}\label{fig:3xdecrease}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_15xdecrease.png}  %BJC9: z_variance = 3.4 angstroms
  \caption{}\label{fig:15xdecrease}
  \end{subfigure}
  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing thermal noise in the z-direction,
  however the $q_r$ cross-section profile does not change. (a) The maximum intensity of R-$\pi$ is ca. 20 
  when we use the same level of noise present in the atomistic simulation. (b) The intensity of R-$\pi$ 
  decreases by a factor of 3, relative to the background intensity, if we increase thermal noise by 11\% 
  in the $z$-direction. (c) The intensity of R-$\pi$ decreases by a factor of 15, relative to the background
  intensity, when we increase thermal noise by 28\% in the $z$-direction.}\label{fig:znoise}
  \end{figure}

  When we allow monomer columns to move independently in the z-direction, the intensity
  of R-$\pi$ drops and the $q_r$ cross-section of the simulated diffraction patterns 
  smooths out. We created simple systems with varying amounts of association between columns. 
  In the low limit, the center of mass of columns are situated at the same z coordinate. 
  This is how all simple systems have been created up to this point. We allow increasing 
  independence of columns by randomly shifting each column in the $z$-direction using a uniform
  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ is between 0 and 1. We
  limit this discussion to configurations close to a sandwiched configuration since it is not
  feasible for columns in the parallel displaced configuration, as we have set them up, to move
  past each other. Allowing columns to move independently smooths out the $q_r$ cross-section
  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in sharp peaks. The
  intensity of R-$\pi$ decreases with increasing column independence. We see an 8 fold decrease
  in the intensity of R-$\pi$ when $f=1$ versus when $f=0$.

@@

  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$ cross-section of R-$\pi$
  to decrease.
  \begin{itemize}
    \item $q_r$ cross-section still too broad
    \item Adding more thermal noise sharpens it
    \item Figure: Overlay thinner FWHM plot on top of wider FWHM 
  \end{itemize}

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{qy_fwhm.png}
  \caption{}\label{fig:qy_fwhm}
  \end{figure}

%MRS9: the statement below is pretty strong, need to back it up.  We know that we have quenched noise, which is a type of over-ordering - is that taken into account?  
  We have nearly the right amount of disorder / noise in our system, but correlation 
  between columns really messes up R-$\pi$.

>>>>

  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections of R-$\pi$ 
  are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}). The
  FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the $q_r$ cross-section
  FWHM is 21\% larger than experiment. Note that the experimental data is best fit with a Lorentzian 
  function while the simulated patterns are best fit using a Gaussian function. The simulated
  spectra do not incorporate the effects of finite domain sizes, pressure broadening and instrumental broadening
  which would alter the peak shape. In the absence of these and other peak broadening effects,
  the experimental peak would actually be narrower, further increasing the discrepancy with simulation.

  %MRS9: State explicitly in what way the discrepancy would increase, i.e. experimental FWHM are broadened by other source (doppler pressure, insttrument broadening) that do no affect the simulated spectra, the experimental spectra may be even narrower than spectra generated from simulations are.  
  %MRS9: one question, do any of the approximations used in the simulation actually lead to broadening that would not be in experiment (gaussian scatterers, etc.  Also, (semi-related) do Gaussian scatters lead to Gaussian peaks? Fourier transforms of Gaussians are Gaussians) 
  % BJC8: Can add more detail about different types of broadening - instrument / finite resolution broadening (for
  % experimental case), doppler (gaussian shaped) and pressure broadening (Lorentzian shaped)
  % See: https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-7
  %MRS 9: it is a little problematic to use two different types of fit, as the FWHM is a little different for each of then. Would lead to slight discrepancies from that.  FWHM is a natural scale parameter for Lorenzians, but not really for Gaussian.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.194 $\pm$ 0.013 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.962 $\pm$ 0.010 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \caption{
  In experiments ((a) and (b)), (a), R-$\pi$ broadens in the $q_z$ direction with a FWHM of 
  0.110 $\pm$ 0.003 $\AA^{-1}$ when fit with a Lorentzian function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792 
  $\pm$ 0.009 $\AA^{-1}$ when fit with a Lorentzian function. In our simulations ((c) and (d)), (c) the FWHM of R-$\pi$ in
  the $q_z$ direction is 0.194 $\pm$ 0.013 $\AA^{-1}$ when fit with a Gaussian function, nearly twice the width
  of experiment. (d) The simulated FWHM in the $q_r$ direction is 0.962 $\pm$ 0.01 $\AA^{-1}$ when fit with
  a Gaussian function, about 20 \% larger than experiment. Note that the large spike in the center is not included
  in the fit.}\label{fig:rpi_exp_comparison}
  \end{figure}

  We have identified a number of potential ways that simulation conditions, forcefield 
  and initial configurations could affect the intensity of R-$\pi$ as well as its FWHM in 
  the $q_z$ and $q_r$ directions. We assessed each using a simplified model. Our 
  simplified model represents each monomer head group as a single point and places them
  in either a parallel displaced or sandwiched configuration. We chose to explore
  the influence of thermal noise in each dimension, the effect of $z$-direction distance correlations
  between scatterers within columns, as well as correlation between columns since these are the variables we 
  believe have the largest influence on peak shape and intensity.
  %MRS9: probably best to focus on the variables that we think could cause a problem (i.e. hypotheses to test) first, then talk about how the experiments tested these hypotheses.

  As a baseline, we created a simplified model using the same amount of disorder present
  in our atomistic simulations. There are two sources of disorder to consider: thermal motion of
  atoms and quenched disorder which is created by rapid structural rearrangement during
  early equilibration and is largely locked into place for the remainder of the simulation. The
  latter has important implications for the reproducibility of this work since both initial
  configurations and velocity randomization at the beginning of equilibration can lead to
  different quenched configurations. We measured thermal disorder by calculating the standard 
  deviation of the distribution of head group center of mass positions from their average 
  positions. We measured quenched disorder by calculating the standard deviation of the 
  distribution of head group center of masses from their idealized average positions. In the
  $z$-direction, we measured the deviation of the head group center of masses from an equally
  spaced column of head groups. In the $xy$ plane, we calculated the deviation in radial 
  position from the pore center and the angular deviation from equally spaced points surrounding
  the pore center. The values measured for each system and type of disorder are given in 
  Table~\ref{table:quenched_disorder}.

  The intensity of R-$\pi$ can be calculated from a single trajectory of uncorrelated
  configurations rather than as the average of multiple correlated trajectories. Theoretically,
  in order to mimic the simulated system, we should build an initial configuration which 
  has the same amount of quenched disorder as our simulations and then create a trajectory
  to which we add thermal disorder to the initial configuration in order to create each frame.
  %BJC9 : The following numbers need to be updated: I want to do 40 trajectories with 1000 frames each for both types of trajectories and compare their mean and uncertainty
  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this way was 
  16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000 initial configurations,
  the intensity of R-$\pi$ is 16.42, in close agreement with the mean of 40 simulations. 
  We use the latter method for the remainder of this work since we can extract the trends
  we need using a single trajectory at a fraction of the computational cost.

  When we simulated the diffraction pattern of a simple system trajectory of 1000 independent
  configurations, each created using the parameters for thermal and quenched disorder in order to place 
  points, the $q_r$ and $q_z$ profiles of R-$\pi$ are characterized by sharp peaks. We made
  this simple system, and all to follow, 4 times taller in the $z$-direction in order to access
  higher $q_z$ resolution. Figure~\ref{fig:sf_qy_nocorrelation} and~\ref{fig:sf_qz_correlation}
  shows the $q_y$ and $q_z$ cross-sections of R-$\pi$ generated by simulating the structure 
  factor of the trajectory. The distance between peaks in the $q_y$ cross-section is equal
  to the distance between pores in real space.

@@

%MRS9: sorry, I keep reading ``no correlation'' as ``no collusion'' :)
%BJC9: haha^
%BJC9: I could probably get rid of qy cross-sections and inset in (c)
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
  \caption{}\label{fig:sf_qy_nocorrelation}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
  \caption{}\label{fig:sf_qy_correlation}
  \end{subfigure} 
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
  \caption{}\label{fig:sf_qz_correlation}
  \end{subfigure}   
  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
  points meant to represent monomer head groups. We added a similar amount of noise to 
  that seen in our simulations. (a) We added Gaussian noise to each particle in the $z$, 
  $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
  peaks. (b) When we correlate the distance between points within each column, the 
  intensity of R-$\pi$ increases but the sharp peaks remain with the same ratio of
  intensity between the center and outer peaks. (c) Correlation of the distance between
  scatterers in the $z$-direction causes R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
  \end{figure}

  The distances between scatterers within each column are correlated with each other.
  In the simplified system described above, we added Gaussian noise to the 
  mean positions of an equally spaced column of points. This ignores any interaction
  head groups might have with each other. To remedy this, we drew random samples from 
  a multivariate normal distribution defined by the mean positions of an equally spaced
  column of points. We gave the distribution at each point along the column the same
  standard deviation, $\sigma_z$, shown  in by Table~\ref{table:quenched_disorder}. We 
  defined a covariance matrix such that the covariance, v, in the distance, z, between
  scatterers decays exponentially from v according to the equation $ve^{-z/L}$, where L
  is the correlation length. Experimentally, the correlation length can be estimated as
  the inverse of the FWHM of the $q_z$ cross-section of R-$\pi$.  %BJC8: needs references 
  Accordingly, the correlation length of the experimental system is $\geq$ 9 
  $\AA$. The value may be larger since the peak is likely broadened for a variety
  of other reasons. We simulated the structure factor of a simple system built as described
  above with a correlation length of 30 $\AA$. We chose 30 $\AA$ in order to exaggerate
  the effect of correlation length for visual purposes. Subsequent structure factor calculations
  are all done with a correlation length of 9 $\AA$. The shape of the $q_y$ cross-section 
  (Figure~\ref{fig:sf_qy_correlation}) remains the same while the the $q_z$ cross-section
  (Figure~\ref{fig:sf_qz_correlation}) broadens, as seen in experiment. Additionally, there
  is a near 20 \% increase in the maximum intensity of R-$\pi$ when the distances between
  scatterers are correlated.

  %BJC8: Can show correlation effect on intensity in supporting info

@@

  Increased thermal noise in the $z$-direction causes a drop in the intensity of R-$\pi$, however 
  the $q_r$ profile remains unchanged. When we increase the thermal noise in the $z$-direction by
  12\% and 27\%, we see a 3 and 15-fold decrease in the maximum intensity of R-$\pi$ respectively (Figure
  ~\ref{fig:znoise}). Despite the decrease in intensity, the 3 cross-sections have the same shape
  (Figure~\ref{fig:rpi_xsection_vs_zsigma}, whose sharp Bragg-like peaks are not consistent with 
  experiment.

  % BJC9: Might be worth acknowledging:
  % The peaks are spaced apart according to the pore spacing, and line up with R-alkanes.

%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{0.3\textwidth}
%  \includegraphics[width=\textwidth]{sf_qy_correlation_L10.png}  %BJC9: z_variance = 2.074 angstroms
%  \caption{}\label{fig:sf_znoise_control}
%  \end{subfigure}
%  \begin{subfigure}{0.3\textwidth}
%  \includegraphics[width=\textwidth]{sf_qy_3xdecrease.png}  %BJC9: z_variance = 2.65 angstroms
%  \caption{}\label{fig:3xdecrease}
%  \end{subfigure}
%  \begin{subfigure}{0.3\textwidth}
%  \includegraphics[width=\textwidth]{sf_qy_15xdecrease.png}  %BJC9: z_variance = 3.4 angstroms
%  \caption{}\label{fig:15xdecrease}
%  \end{subfigure}
%  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing thermal noise in the z-direction,
%  however the $q_r$ cross-section profile does not change. (a) The maximum intensity of R-$\pi$ is ca. 20 
%  when we use the same level of noise present in the atomistic simulation. (b) The intensity of R-$\pi$ 
%  decreases by a factor of 3, relative to the background intensity, if we increase thermal noise by 11\% 
%  in the $z$-direction. (c) The intensity of R-$\pi$ decreases by a factor of 15, relative to the background
%  intensity, when we increase thermal noise by 28\% in the $z$-direction.}\label{fig:znoise}
%  \end{figure}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{intensity_vs_zsigma.png}
  \caption{}\label{fig:intensity_vs_zsigma}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{rpi_xsection_vs_zsigma.png}
  \caption{}\label{fig:rpi_xsection_vs_zsigma}
  \end{subfigure}
  \caption{We can decrease the maximum intensity of R-$\pi$ by increasing thermal noise in the z-direction,
  however the $q_r$ cross-section profile does not change. (a) The intensity of R-$\pi$ drops precipitously
  as we increase $\sigma_z$. We can decrease the intensity of R-$\pi$, relative to the background intensity
  as seen in our simulation (blue) by a factor of 3 when we increase $\sigma_z$ by 12\% (green) and by a factor of 15 when we increase 
  $\sigma_z$ by 27 \% (red). (b) Although the maximum intensity of R-$\pi$ decreases with increasing $\sigma_z$,
  the peak shape remains the same.}\label{fig:znoise}
  \end{figure}

  When we allow monomer columns to move independently in the z-direction, the intensity
  of R-$\pi$ drops and the $q_r$ cross-section of the simulated diffraction patterns 
  smooths out. We created simple systems with varying amounts of association between columns. 
  In the low limit, the center of mass of columns are situated at the same $z$-coordinate. 
  This is how all simple systems have been created up to this point. We allow increasing 
  independence of columns by randomly shifting each column in the $z$-direction using a uniform
  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges between 0 and 1. We
  limit this discussion to the sandwiched configuration since it is not
  feasible for columns in the parallel displaced configuration, as we have set them up, to move
  past each other. The trends seen above apply to both the sandwiched and parallel displaced systems.
  Allowing columns to move independently smooths out the $q_r$ cross-section
  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in sharp peaks. The
  intensity of R-$\pi$ decreases with increasing column independence. We see an 8-fold decrease
  in the intensity of R-$\pi$ when $f=1$ versus when $f=0$.

@@

  Increasing thermal noise in the $xy$ plane causes the FWHM of the $q_r$ cross-section of 
  R-$\pi$ to decrease. We modified the disorder in both the $r$ and $\theta$ directions by
  multiplying their values by a factor of 0.5 and 2 (Figure~\ref{fig:qy_fwhm}). When we cut
  the noise in half, the FWHM increases by 88 \%. When we double the noise, the FWHM 
  decreases by 51 \%.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{qy_fwhm.png}
  \caption{Increasing the amount of disorder in the $xy$ plane decreases the FWHM of the 
  $q_y$ cross-section of R-$\pi$. When we cut the amount of $r$ and $theta$ disorder in
  half (Noise factor = 0.5), the FWHM increases by 88\%. When we double the disorder 
  (Noise factor = 2), the FWHM decreases by 51\%.}\label{fig:qy_fwhm}
  \end{figure}

  We can use what we learned above in order to construct a better model, however there
  will still be shortcomings. We can decrease the intensity of R-$\pi$ if we incorporate
  more $z$-directional noise, which may come from increasing the system's temperature.
  % BJC9: Is there actually a good way to increase thermal noise in the z-direction without
  % temperature? Is decreasing the force constant between bonds viable? 
  We can adjust the parameters for aromatic carbons so that head groups stack more 
  closely together. Perhaps the simplest thing to do is to create initial configurations
  whose columns are displaced randomly in the $z$-direction in order to mimic independence.
  Ultimately, we will need extremely long simulation times so that monomers within 
  columns can rearrange and sample enough independent configurations to generate a robust
  simulated XRD pattern.

  The architecture of each column is likely somewhere between sandwiched and parallel 
  displaced. The parallel displaced configuration that we have simulated in this paper
  is an exaggerated manifestation of the parallel displaced $\pi-\pi$ stacking mode. 
  The simulated XRD pattern shows faint off-axis features at the same $q_r$ value as
  R-double which is only in patterns generated from parallel displaced configurations. 
  The monomers may prefer to be parallel displaced, but their displacement is likely 
  only slightly shifted, on the $xy$ plane, from the center of mass of their vertically
  adjacent neighbors. In this way, columns can more easily act independently while 
  maintaining a parallel displaced structure.
